HMMotion: Using tracking data to predict coverage strategies in American Football

### 2025-01-06 submission.Rmd
.

@@

<!-- <div style="text-align: center;"> -->
<!--   ![](AUCs_bdb_main.png) -->
<!-- </div> -->

@@

The plots above show the results for our 50 repetitions of the experiment. First, we show the classification accuracy, when using a threshold of 50\%. Since this is an arbitrary value and our data is slightly imbalanced ($\approx$ 75\% zone coverage plays and $\approx$ 25\% man coverage plays), accuracy is not the best metric for analyzing the results. Therefore, we also present the AUC values of the model (see Appendix for a discussion on evaluation metrics). For both metrics, we notice a few things. On the one hand, the more flexible `xgboost` model performs better than the `glmnet`. However, there is more variation for the `xgboost` model, suggesting that more data would help improve the tuning of the models. On the other hand, the pre-motion model clearly performs worst. As soon as we incorporate motion information, there is a large increase in performance. While this is expected, we also see that the HMM post-motion model outperforms the model with only naive post-motion information. This shows that the HMM features capture information, which is distinct from simple motion features and provide another dimension of information, which needs to be incorporated.

@@

@@

>>>>

`r colorize("Den Text finde ich irgendwie unrund und nicht so leicht verständlich.","red")`

@@

@@

The plots above show the results from our 50 repetitions of the experiment. The first figure illustrates classification accuracy, using a threshold of 50\%. Since this value is somewhat arbitrary and our dataset is slightly imbalanced ($\approx$ 75\% zone coverage plays and $\approx$ 25\% man coverage plays), accuracy is a suboptimal metric for evaluating the results. Hence, we also present the AUC values of the three models (see Appendix for a discussion on evaluation metrics). 
Several observations emerge from these metrics. On the one hand, the more flexible `xgboost` model outperforms `glmnet`, but it also exhibits greater variation, indicating that additional data could enhance the tuning of this model. 
On the other hand, the pre-motion model performs the worst. However, once motion information is incorporated, we observe a substantial improvement in performance.
While this is to be expected, we also see that the HMM post-motion model outperforms the model with only naive post-motion information. This indicates that the HMM features capture distinct information beyond simple motion features, providing an additional dimension that enhances the overall analysis.

@@

`r colorize("Die figure fehlt irgendwie noch","red")`

@@

`r colorize("Von chatGPT:","red")`

This project explored the use of hidden Markov models (HMMs) to enhance the prediction of defensive schemes in football by incorporating pre-snap player movements. Models augmented with HMM-derived features demonstrated improved predictive performance compared to those relying solely on naive motion data. The HMM effectively captured latent defensive behaviors, offering deeper insights into the defenders' actions.

The HMM features allowed for more effective inference of guarding assignments, improving the distinction between man and zone coverage. This improvement underscores the HMM's capacity to model the dynamic and often subtle nature of defensive strategies, capturing patterns that simple motion features cannot.

Looking ahead, the potential of HMMs goes beyond predicting man or zone defense. They could be applied to decode complex guarding assignments and analyze defensive adjustments in real-time, providing a powerful tool for deeper strategic insights in sports analytics.
